Contribution Title\thanks{Supported by organization x.}

### 2019-05-05 main.tex
Write abstract.

\begin{document}
%
\title{Contribution Title\thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Akira Kawata\inst{1} \and
Atsushi Igarashi\inst{2}\orcidID{0000-0002-5143-9764}}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Graduate School of Informatics, Kyoto University, Kyoto, Japan\\
\email{akira@kuis.kyoto-u.ac.jp} \and
\email{igarashi@kuis.kyoto-u.ac.jp}
}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
The abstract should briefly summarize the contents of the paper in
150--250 words.
\keywords{Multistage programming \and Dependent type \and Specification verification by tests.}
\end{abstract}
%
%
%
\section{First Section}
\subsection{A Subsection Sample}
Please note that the first paragraph of a section or subsection is
not indented. The first paragraph that follows a table, figure,
equation etc. does not need an indent, either.

>>>>

\begin{document}
%
\title{Contribution Title\thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Akira Kawata\inst{1} \and
Atsushi Igarashi\inst{2}\orcidID{0000-0002-5143-9764}}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Graduate School of Informatics, Kyoto University, Kyoto, Japan\\
\email{akira@kuis.kyoto-u.ac.jp} \and
\email{igarashi@kuis.kyoto-u.ac.jp}
}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
We develop yet another typed multi-stage calculus Lambda-MD. It extends Hanada and Igarashi's Lambda-TP with dependent type.

Multi-stage calculus enables us to generate and execute codes at runtime. And people have researched it as a method for improving the performance of programs. On the other hand, the dependent type is a type dependent on values. It is famous for its application for vectors with their length.

In this article, we design Lambda-MD by introducing dependent type into Lamda-TP. It has a simple, substitution-based full-reduction semantics and enjoys basic properties of subject reduction, confluence, and strong normalization. In addition, we define an evaluation context which takes stages into account. Under the evaluation context progress is hold.

As a result of the combination of multi-stage calculus and dependent type, we can test code-generating functions such as staged interpreter at type-checking time. Staged-interpreter takes an abstract syntax tree as its input and output a corresponding code. Using dependent type, we can check whether some conditions written as a term is true or not at type-checking time. Then we can check staged-interpreter returns the correct output for a given input.

199 words

The abstract should briefly summarize the contents of the paper in
150--250 words.
\keywords{Multistage programming \and Dependent type \and Specification verification by tests.}
\end{abstract}
%
%
%
\section{First Section}
\subsection{A Subsection Sample}
Please note that the first paragraph of a section or subsection is
not indented. The first paragraph that follows a table, figure,
equation etc. does not need an indent, either.
